---
title: "Youtube Trending Videos 4-24-18"
author: "Sean Nguyen"
date: "May 18, 2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
library(tidyverse)
library(lubridate)
library(wordcloud)
yt <- read_csv("data 4-24/USVideos.csv")
```

## Popular Videos

### Most Viewed Videos Today
```{r}
yt %>% arrange(desc(views)) %>% .[1:10,] %>% select (title, channel_title, views) %>% rename(Video=title, Channel=channel_title, Views=views) %>% mutate(Rank=seq.int(nrow(.))) %>% select(Rank, Video, Channel, Views) %>% knitr::kable(.)
```

### Views vs Likes
```{r}
ggplot(data=yt) + geom_jitter(mapping = aes(x = views/1000000, y = likes/1000000)) + labs(x="Views (Millions)", y="Likes (Millions)") + scale_x_continuous(labels = scales::unit_format(unit="M")) + scale_y_continuous(labels = scales::unit_format(unit="M"))
```

Likes increase logarithmically with views, suggesting that earlier viewers are more likely to react (e.g. subscribers), while later viewers are less interested (maybe the video is on the Trending page at this point).
The data points follow several distinct curves, which suggests that certain types of videos get more likes per view than others.

```{r}
ggplot(data=yt) + geom_jitter(mapping = aes(x = views, y = likes), color="green") + geom_jitter(mapping = aes(x = views, y = dislikes), color="red")

```

## Popular Channels

### Channels With Most Trending Videos
```{r}
yt_by_channel <- group_by(yt, channel_title) %>% summarise (channel_videos = n(), channel_views = sum(views)) %>% mutate(views_per_video = channel_views / channel_videos) %>% arrange(desc(channel_videos))

yt_by_channel$channel_title <- factor(yt_by_channel$channel_title, levels = yt_by_channel$channel_title[order(yt_by_channel$channel_videos)])

yt_by_channel %>% arrange(desc(channel_videos)) %>% .[1:10,] %>% ggplot + geom_col(aes(x=channel_title, y=channel_videos, fill=channel_videos)) + coord_flip() + labs(x="Channel", y="# of Trending Videos") + theme(legend.position="none")
```

Most of the top 10 channels are sports channels or talk shows. Channels like ESPN have a broad appeal and often post lots of short clips each day.

### Average Views Per Video
```{r}
yt_by_channel$channel_title <- factor(yt_by_channel$channel_title, levels = yt_by_channel$channel_title[order(yt_by_channel$views_per_video)])

yt_by_channel %>% arrange(desc(views_per_video)) %>% .[1:10,] %>% ggplot + geom_col(aes(x=channel_title, y=views_per_video/1000000, fill=views_per_video)) + coord_flip() + labs(x="Channel", y="Views Per Video (Millions)") + scale_y_continuous(labels = scales::unit_format(unit="M")) + theme(legend.position="none")
```

Mostly mainstream music, except for Kylie Jenner and YouTube Spotlight.




## Trending Over Time

Most videos start trending after about a week, but it can sometimes take years:
```{r}
yt <- mutate(yt,publish_date=as.Date(publish_time), trending_as_date=as.Date(trending_date, "%y.%d.%m"))
yt <- mutate(yt, days_to_trend=as.integer(trending_as_date - publish_date))
yt <- mutate(yt, days_trending = as.integer(as.Date("2018-04-24", "%Y-%m-%d") - trending_as_date))

yt %>% ggplot + geom_density(mapping=(aes(x=log10(days_to_trend+1))), adjust=2) +
  geom_vline(aes(xintercept=log10(7+1)), color="blue", linetype="dashed") + 
  annotate("text", x=1, y=.25, label="7 days", angle=90, color="blue") +
  scale_x_continuous(breaks=waiver(), labels=c(0,10,100,1000,10000))  + 
  labs(title="Time to Trend",x="Days Since Upload")
```

Some videos even trend the same day:
```{r}
yt %>% filter(days_to_trend <= 7) %>% ggplot + geom_bar(mapping=(aes(x=days_to_trend))) + labs(title="Trending First Week", x="Days Since Uploaded")
```

Today's Trending videos have been trending for anywhere from 0 to 5 months:
```{r}
yt %>% ggplot + geom_histogram(mapping=aes(x=days_trending, alpha=..count..), binwidth=10, center=5, color="black") + scale_x_continuous(breaks=seq(0,180,20)) + theme(legend.position="none") + labs(title="How Long Videos Have Been Trending", x="Days")
```

Some videos uploaded in the early 2000s are still trending today, but the vast majority of today's trending videos were uploaded within the past 12 months.

```{r}
ggplot(yt) + geom_freqpoly(mapping=aes(x=publish_time)) +
    scale_x_datetime(limits = c(as.POSIXct("2005-01-01"), as.POSIXct("2016-12-31"))) + labs(title="Uploaded 2005-2016", x="Upload Date")

ggplot(yt) + geom_freqpoly(mapping=aes(x=publish_time)) +
  scale_x_datetime(date_breaks="2 months", date_labels="%b", limits = c(as.POSIXct("2017-04-25"), as.POSIXct("2018-04-25"))) + labs(title="Uploaded 2017-2018", x="Month")

```